\subsection*{ASP.NET Core}
a cross-platform, high-performance, open-source framework for building modern, cloud-enabled, Internet-connected apps.
\subsection*{ASP.NET Core MVC}
A lightweight, open source, highly testable presentation framework optimized for use with ASP.NET Core.
\subsection*{Unity}
A cross-platform game engine developed by Unity Technologies with the goal to provide developers with the tools to make game development simple
\subsection*{Unity XR}
A cross-platform plugin used for virtual, mixed, and augmented reality. XR Interaction Toolkit provides easy built-in functionality to select, grab, throw, rotate objects within a VR scene
\subsection*{\C}
(pronounced "See Sharp") A modern, object-oriented, and type-safe programming language. \C enables developers to build many types of secure and robust applications that run in .NET. \C has its roots in the C family of languages and will be immediately familiar to C, C++, Java, and JavaScript programmers.
\subsection*{LINQ}
Language-Integrated Query (LINQ) is the name for a set of technologies based on the integration of query capabilities directly into the \C language. 
\subsection*{Entity Framework Core}
Entity Framework (EF) Core is a lightweight, extensible, open source and cross-platform version of the popular Entity Framework data access technology.
\subsection*{SQL Server}
SQL Server is a relational database management system, or RDBMS, developed and marketed by Microsoft.
\subsection*{Transparent Data Encryption (TDE)}
Transparent data encryption (TDE) encrypts SQL Server, Azure SQL Database, and Azure Synapse Analytics data files. This encryption is known as encrypting data at rest.
\subsection*{Basic Authentication}
In the context of an HTTP transaction, basic access authentication is a method for an HTTP user agent (e.g. a web browser) to provide a user name and password when making a request. In basic HTTP authentication, a request contains a header field in the form of \lstinline{Authorization: Basic <credentials>}, where credentials is the Base64 encoding of ID and password joined by a single colon :.
\subsection*{JSON}
JSON stands for JavaScript Object Notation. JSON is a lightweight format for storing and transporting data. JSON is often used when data is sent from a server to a web page
\subsection*{HTTPS}
Hypertext transfer protocol secure (HTTPS) is the secure version of HTTP, which is the primary protocol used to send data between a web browser and a website. HTTPS is encrypted in order to increase security of data transfer. 
\subsection*{REST}
REST, or REpresentational State Transfer, is an architectural style for providing standards between computer systems on the web, making it easier for systems to communicate with each other. REST-compliant systems, often called RESTful systems, are characterized by how they are stateless and separate the concerns of client and server
 \subsection*{CSS}
CSS stands for Cascading Style Sheets which describes how HTML elements are to be displayed on screen, paper, or in other media
\subsection*{HTML}
Hypertext Markup Language (HTML), a standardized system for tagging text files to achieve font, color, graphic, and hyperlink effects on World Wide Web pages.
\subsection*{Bootstrap}
Bootstrap is the most popular CSS Framework for developing responsive and mobile-first websites.
\subsection*{Web API}
Web API is an application programming interface (API) is a set of subroutine definitions, protocols, and tools for building software and applications over the web which can be accessed using HTTP protocol.
\subsection*{GUID}
A globally unique identifier (GUID) is a 128-bit number created by the Windows operating system or another Windows application to uniquely identify specific components, hardware, software, files, user accounts, database entries and other items.
\subsection*{Git}
Git is a free and open source distributed version control system designed to handle everything from small to very large projects with speed and efficiency.
\subsection*{Dependency Injection}
Dependency injection is a programming technique that makes a class independent of its dependencies. It achieves that by decoupling the usage of an object from its creation.
\subsection*{Razor View Engine}
Razor View engine is a markup syntax which helps us to write HTML and server-side code in web pages using \C.
\subsection*{Visual Studio}
Microsoft Visual Studio is an integrated development environment (IDE) from Microsoft. It is used to develop computer programs, as well as websites, web apps, web services and mobile apps.
\subsection*{Unity Editor}
 Unity Editor is the IDE to enable Unity development. Unity is a game development platform used to build high-quality 3D/2D games that can deployed across mobile, desktop, VR/AR, consoles, or the web.
\subsection*{Cross Site Scripting (XSS)}
Cross Site Scripting (XSS) attacks are a type of injection, in which malicious scripts are injected into otherwise benign and trusted websites. XSS attacks occur when an attacker uses a web application to send malicious code, generally in the form of a browser side script, to a different end user.
\subsection*{SQL Injection}
A SQL injection attack consists of insertion or ``injection” of a SQL query via the input data from the client to the application. A successful SQL injection exploit can read sensitive data from the database, modify database data (Insert/Update/Delete), execute administration operations on the database (such as shutdown the DBMS), recover the content of a given file present on the DBMS file system and in some cases issue commands to the operating system. SQL injection attacks are a type of injection attack, in which SQL commands are injected into data-plane input in order to affect the execution of predefined SQL commands.
\subsection*{xUnit}
xUnit.net is a free, open source, community-focused unit testing tool for the .NET Framework. 

